Target Markdown

### 2023-04-27 _targets.Rmd
dd

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector))

>>>>

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
     tar_target(random_pubs,
           get_random_pubs(db_path))
)
```
